\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage{url}
\usepackage{mathabx}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\topmargin=0in
\topskip=0in
 
 
\newenvironment{list1}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\blackdiamond$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\begin{document}

\name{\LARGE Debamitro Chakraborti}

\begin{resume}

%%%%%%%%%%%%%%%%%%%

\section{\sc Contact}
%%%%%%
E-mail: {\em debamitro@gmail.com} \\
Website: \href{https://debamitro.github.io/}{https://debamitro.github.io}
%%%%%%

\section{\sc Now}
%%%%%%
{\bf Self-employed} \\ \\
At present I am figuring out how to solve real human problems using my tech skills.
\begin{list1}
    \item Building a child care web app for busy parents, as part of the Born to Thrive team
    \item Building a cross-platform email management tool in Rust
    \item Building small LLM-powered projects
\end{list1}
%%%%%%

\section{\sc Professional Experience}
%%%%%%
{\bf   Cadence Design Systems} \\ \\
{\bf Xcelium} \\
This product simulates hardware by compiling gigabytes of high level source code. Even the most complex chips in the world use this product. It is best to describe this product as a compiler tool-chain
for a complex high-level language which is only used to create massive codebases. Before you ask, yes this is how GPUs are designed. \\ \\
{\bf Software Architect}
\hfill{\bf August 2024 - December 2024} \\ \\
Paving the path for Xcelium runtime performance improvements for the next decade
%%%%%%

%%%%%%
{\bf Senior Principal Software Engineer}
\hfill{\bf October 2020 - July 2024} \\
\begin{list1} %Job Description%
    \item Leading a team of engineers working on Xcelium performance
    \item Technical lead for a brand new optimization engine for Xcelium
    \item Working to speed up Xcelium for faster verification of next-generation hardware designs
\end{list1}
%%%%%%

%%%%%%
{\bf Principal Software Engineer}
\hfill{\bf August 2010 - September 2020} \\
\begin{list1} %Job Description%
		\item Optimized the runtime performance of the simulator by as much as 10x in various critical customer designs.
		\item Improved the peak memory usage of the compiler by as much as 30\%.
		\item Wrote IR-based compiler optimizations including function inlining for the System Verilog language.
		\item Implemented new scheduling semantics in the simulator.
		\item Designed and developed various parts of the runtime library of the simulator.
		\item Refactored legacy code in a \~10MLOC codebase.
   		\item Started introducing modern C++ in the team and organized technical learning sessions.
   		\item Took initiative for improving the build system to make it faster by parallelization.
\end{list1}
%%%%%%

{\bf  Nusym Technology India Pvt Ltd}
\hfill {\bf R\&D Engineer}
\hfill{\bf October 2008 - June 2010}
\vspace{.05in}
\begin{list1} %Job Description%
	\item Developed various parts of the interpreted simulator.
\end{list1}
%%%%%%
{\bf  Atrenta India Pvt Ltd}
\hfill {\bf Senior Software Engineer}
\hfill{\bf July 2005 - October 2008}
\vspace{.05in}
\begin{list1} %Job Description%
\item Worked on the core engine of a static analysis tool.
\end{list1}
%%%%%%%

%\vspace{.5in}
\section{\sc Technical Skills}
\begin{list1}
	\item Well-versed in modern web app stacks
	\item Extensive knowledge of C and C++
	\item Some experience with Rust and Clojure/ClojureScript
\end{list1}

\section{\sc Publications}
\begin{list1}
	\item \href{https://www.researchgate.net/publication/229005723_PRIVDAM_Privacy_Violation_Detection_and_Monitoring_Using_Data_Mining}{'PRIVDAM: privacy violation detection and monitoring using data mining'}
by Jaijit Bhattacharya, Rajanish Dass, Vishal Kapoor, Debamitro Chakraborti, S.K. Gupta.
(Working paper, IIM Ahmedabad, 2005)
\end{list1}

\section{\sc Undergrad Projects}
\begin{list1}
	\item Implemented a set of new real-time data mining algorithms and benchmarked them on standard datasets. Language: C++/STL. Advisor: Prof Rajanish Dass, IIM Ahmedabad.
	\item Developed the Linux version of  \href{http://www.bangla.name/isis}{Indian Script Input System}, a program that enables users to phonetically type Indic scripts on both Windows and Linux. The typing system was invented by Prof Gautam Sengupta, University of Hyderabad. Language: C/C++. GUI: GTK for gnome, Xlib for X.
	\item Developed a MIDI file generator for programmatically generated music, and presented it at the Engineering and Technological Fair held at Birla Industrial and Technological Museum in February 2001. Language: C.
	\item Developed the GUI for a gsm network simulation project. Language: C++ with Qt.
	\item Wrote an evaluation engine for temporal logic formulae, as part of a project on Formal Verification of Security Protocols using Temporal Logic. Language: C++. Advisor: Prof Chandan Majumdar, CSE, Jadavpur University.
\end{list1}

\section{\sc Education and awards}
\begin{list1}
	\item Recurse Center, New York City (Mini batch, August 2018)
	\item B.E. in Computer Science and Engineering (year: 2005)
from Jadavpur University, Kolkata (percentage: 75)
	\item 5th rank in West Bengal Joint Entrace Examination (2001)
	\item Jagadis Bose National Science Talent Search scholar (batch of 2001)
\end{list1}

\end{resume}
\end{document}